---
title: "Automating Project 2"
author: "Laura Mathews"
date: "10/14/2020"
output: 
  rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Code needed to change to readme.md:

#render("Project-2-Automation.md", output_file = "README.md")
```

# Purpose of this repository:

The purpose of this repository is to use two different tree models to predict bike useage count for each day of the week. Data on bike sharing was analyzed to create the models. The reports for each week were then automated.

+ The analysis for [Monday is available here](MondayAnalysis.md).
+ The analysis for [Tuesday is available here](TuesdayAnalysis.md).
+ The analysis for [Wednesday is available here](WednesdayAnalysis.md).
+ The analysis for [Thursday is available here](ThursdayAnalysis.md).
+ The analysis for [Friday is available here](FridayAnalysis.md).
+ The analysis for [Saturday is available here](SaturdayAnalysis.md).
+ The analysis for [Sunday is available here](SundayAnalysis.md).

```{r main-chunk}
#Packages Needed

library(tidyverse)
library(rmarkdown)
library(knitr)

#Create output file names

daynames <- c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")
daynum <- 0:6

output_file <- paste0(daynames, "Analysis.md")

#Put parameters and day names in a list, create a data frame with the parameters, day names, and output file names

params1 <- lapply(daynames, FUN = function(x){list(day = x)})
params2 <- lapply(daynum, FUN = function(x){list(day = x)})

reports <- tibble(output_file, params1, params2)

#Use the render function to create reports

apply(reports, MARGIN = 1,
      FUN = function(x){
        render(input = "Project 2.Rmd", output_file = x[[1]], params = x[[3]])
      })
```